%%%%%%%%%%%%%%%%%
% This is an example CV created using altacv.cls (v1.6, 21 May 2021) written by
% LianTze Lim (liantze@gmail.com), based on the
% Cv created by BusinessInsider at http://www.businessinsider.my/a-sample-resume-for-marissa-mayer-2016-7/?r=US&IR=T
%
%% It may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%    http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%%%%%%%%%%%%%%%


%% Use the "normalphoto" option if you want a normal photo instead of cropped to a circle
% \documentclass[10pt,a4paper,normalphoto]{altacv}

\documentclass[10pt,a4paper,ragged2e,withhyper]{files/altacv}

%% AltaCV uses the fontawesome5 package.
%% See http://texdoc.net/pkg/fontawesome5 for full list of symbols.

% Change the page layout if you need to
\geometry{left=1.25cm,right=1.25cm,top=1.5cm,bottom=1.5cm,columnsep=1.2cm}

% The paracol package lets you typeset columns of text in parallel
\usepackage{paracol}

% Change the font if you want to, depending on whether
% you're using pdflatex or xelatex/lualatex
\ifxetexorluatex
  % If using xelatex or lualatex:
  \setmainfont{Lato}
\else
  % If using pdflatex:
  \usepackage[default]{lato}
\fi

% Change the colours if you want to
\definecolor{VividPurple}{HTML}{000080}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\definecolor{url}{HTML}{0645AD}
% \colorlet{name}{black}
% \colorlet{tagline}{PastelRed}
\colorlet{heading}{VividPurple}
\colorlet{headingrule}{VividPurple}
% \colorlet{subheading}{PastelRed}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Change some fonts, if necessary
% \renewcommand{\namefont}{\Huge\rmfamily\bfseries}
% \renewcommand{\personalinfofont}{\footnotesize}
% \renewcommand{\cvsectionfont}{\LARGE\rmfamily\bfseries}
% \renewcommand{\cvsubsectionfont}{\large\bfseries}

% Change the bullets for itemize and rating marker
% for \cvskill if you want to
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%% Use (and optionally edit if necessary) this .tex if you
%% want to use an author-year reference style like APA(6)
%% for your publication list
%\input{pubs-authoryear}

%% Use (and optionally edit if necessary) this .tex if you
%% want an originally numerical reference style like IEEE
%% for your publication list
% \input{pubs-num}

%% sample.bib contains your publications

\begin{document}
\name{IMAN BARZEGARI}
\tagline{Graduate Student in Computer Engineering}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
%% You can add multiple photos on the left or right
%\photoR{2.5cm}{mmayer-wikipedia-cc-by-2_0}
% \photoL{2cm}{Yacht_High,Suitcase_High}

\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{imanbarzegari95@gmail.com}
  \location{Tehran, Iran}
  \homepage{imiiii.github.io/}
  \linkedin{imibarzegari}
  \github{imiiii}
  

%   \orcid{0000-0000-0000-0000} % Obviously making thi\textit{\textit{}}s up too.
  %% You can add your own arbitrary detail with
  %% \printinfo{symbol}{detail}[optional hyperlink prefix]
  % \printinfo{\faPaw}{Hey ho!}
  %% Or you can declare your own field with
  %% \NewInfoFiled{fieldname}{symbol}[optional hyperlink prefix] and use it:
  % \NewInfoField{gitlab}{\faGitlab}[https://gitlab.com/]
  % \gitlab{your_id}
	%%
  %% For services and platforms like Mastodon where there isn't a
  %% straightforward relation between the user ID/nickname and the hyperlink,
  %% you can use \printinfo directly e.g.
  % \printinfo{\faMastodon}{@username@instace}[https://instance.url/@username]
  %% But if you absolutely want to create new dedicated info fields for
  %% such platforms, then use \NewInfoField* with a star:
  % \NewInfoField*{mastodon}{\faMastodon}
  %% then you can use \mastodon, with TWO arguments where the 2nd argument is
  %% the full hyperlink.
  % \mastodon{@username@instance}{https://instance.url/@username}
}

\makecvheader

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Set the left/right column width ratio to 6:4.
\columnratio{0.6}

% Start a 2-column paracol. Both the left and right columns will automatically
% break across pages if things get too long.
\begin{paracol}{2}
\cvsection{Education}
\cvevent{M.S.\ in Computer Engineering - Computer Systems}{ \href{http://en.sbu.ac.ir/SitePages/Home.aspx}
 	{Shahid beheshti University}.}{Sep 2019 -- Ongoing}{}


    \textbf{\textcolor{3}{Thesis:} Exploiting processing in memory for DNN Hardware Acceleration}: I designed and developed a framework for using in-memory processing technology for DNN hardware acceleration.
    
\begin{itemize}    
    \item \textbf{Winner} of national competition for \textbf{research grant} held among all Master's and PhD students. Only 30 projects won the award.
    
\end{itemize}
\divider

\cvevent{B.S.\ in Software Engineering}{ \href{https://www.bzte.ac.ir/en}{Buein Zahra Technical University (Imam Khomeini International University)}}{Sep 2014 -- Jan 2019}{}
% \divider

    \textbf{\textcolor{3}{Final Project:} Learning Management System}: I used the state-of-the-art technology (ASP core for the back-end, angular6 for the front-end, and SQL server to manage the database) to design a fast and simple single-page learning management system. It is composed of three main modules: examing, grading, and evaluation.


\cvsection{Professional Experience}

\cvevent{ Full Stack Developer}{ \href{https://mk4bt.org/}{Marketing for Betterment}}{Oct 2023 -- }{Washington, USA}


\begin{itemize}

\item Developed a \textbf{TypeScript} framework to generate javascript
\item Delevoped an extension for monitoring user interaction in \textbf{ Chrome } and designed the \textbf{Fast API} services to communicate with each other. 




\end{itemize}

\divider 

\cvevent{ ML Adviser}{ \href{https://www.hooshkar.com/}{Hooshkar Pardaz}}{May 2023 -- Sep 2023 }{Tehran, Iran}
\begin{itemize}

\item Worked on a  \textbf{stock brokerage project} ordered by \textbf{Melli Bank}. 

\item implementing a project using the latest technology such as \textbf{Angular13}, \textbf{Stimulsoft} and other needs.
\item build a  \textbf{Forecasting} Project on a \textbf{Blazor} framework using ML.net.


\end{itemize}

\divider

\cvevent{ Software Developer}{ \href{http://vidacomp.ir/}{Deep Thinkers Vida}}{Aug 2015 -- July 2020}{Tehran, Iran}
\begin{itemize}

\item \textbf{Worked on 10+ projects} at various sizes as a full-stack developer, using different frameworks and technologies in the backend and frontend. 

\item Familiar with system design and architecture, software development life cycle, and agile project management. 

\item \textbf{Managed} an \textbf{agile} team of 3 in a fully-tailored Claim Management web application for an insurance company.

\item Comprehensive \textbf{full-stack development} training of \textbf{two interns} during a summer internship program. The training covered front-end and back-end development using \textbf{MVC}, \textbf{EF}, and \textbf{SQL}. EPie hired both interns as full-stack developers following the internship.
\end{itemize}











% \cvevent{Product Engineer}{Google}{23 June 1999 -- 2001}{Palo Alto, CA}

% \begin{itemize}
% \item Joined the company as employe \#20 and female employee \#1
% \item Developed targeted advertisement in order to use user's search queries and show them related ads
% \end{itemize}


\iffalse
\cvsection{A Day of My Life}
% Adapted from @Jake's answer from http://tex.stackexchange.com/a/82729/226
% \wheelchart{outer radius}{inner radius}{
% comma-separated list of value/text width/color/detail}
% Some ad-hoc tweaking to adjust the labels so that they don't overlap
\hspace*{-1em}  %% quick hack to move the wheelchart a bit left
\wheelchart{1.5cm}{0.5cm}{%
  10/13em/accent!30/Sleeping \& dreaming about work,
  25/9em/accent!60/Public resolving issues with Yahoo!\ investors,
  5/11em/accent!10/\footnotesize\\[1ex]New York \& San Francisco Ballet Jawbone board member,
  20/11em/accent!40/Spending time with family,
  5/8em/accent!20/\footnotesize Business development for Yahoo!\ after the Verizon acquisition,
  30/9em/accent/Showing Yahoo!\ \mbox{employees} that their work has meaning,
  5/8em/accent!20/Baking cupcakes
}

% use ONLY \newpage if you want to force a page break for
% ONLY the currentc column
\newpage



\nocite{*}

\printbibliography[heading=pubtype,title={\printinfo{\faBook}{Books}},type=book]

\divider

\printbibliography[heading=pubtype,title={\printinfo{\faFile*[regular]}{Journal Articles}}, type=article]

\divider

\printbibliography[heading=pubtype,title={\printinfo{\faUsers}{Conference Proceedings}},type=inproceedings]

%% Switch to the right column. This will now automatically move to the second
%% page if the content is too long.
\fi
\switchcolumn



\cvsection{Research Experience}
\cvevent{Research Assistant}{ \href{http://www.ipm.ac.ir/}{IPM (Institute For Research In Fundamental Sciences)}}{Oct 2020 -- Ongoing}{Tehran, Iran}
\begin{itemize}
\item  Experience working with DNN frameworks such as \href{https://pytorch.org/}{\textbf{PyTorch}} and \href{https://www.tensorflow.org/}{\textbf{TensorFlow}}.

\end{itemize}


\cvsection{Awards and Honors}

\cvachievement{\faTrophy}{Research Grant}{Winner of national competition for research grant held among all master's and PhD students (2020)}

\divider
    
\cvachievement{\faUsers}{Ranked among top 2\% participants}{National university entrance exam for master's studies (2019)} 



\cvsection{Skills}
\cvtag{Python} \cvtag{C\#}\cvtag{TensorFlow} \cvtag{PyTorch}
\cvtag{Machine Learning}  \cvtag{Deep Learning} \cvtag{ML.net}
\divider

\cvtag{Software/Hardware Co-Design} \cvtag{LLVM}
\cvtag{Caffe2} \cvtag{MLIR}  \cvtag{Glow}\cvtag{ONNX} 

 

\divider

 \cvtag{Debugging} \cvtag{Trello} \cvtag{Scrum}
\cvtag{Ducker Hub} 

\cvtag{Source Control - Git} \cvtag{Swagger}

\divider 

\cvtag{Research} \cvtag{Problem Solving}
\cvtag{Team Work}
\cvtag{Time management} 
\cvtag{Project Management}
\divider

\cvtag{ASP Core} \cvtag{SQL} \cvtag{Entity Framework}
\cvtag{Angular13}   \cvtag{Material Design} \cvtag{Blazor}

\divider 

\cvtag{HTML5} \cvtag{CSS3} \cvtag{Bootstrap} \cvtag{JQuery} \cvtag{JavaScript} \cvtag{AngularJS}
\cvtag{Figma} \cvtag{balsamiq}
 \smallskip \divider
\cvsection{Scores}

\cvachievement{\faCertificate}{TOEFL Total Score: 94}{Reading: 25, Listening: 27,  Speaking: 21,  Writing: 21}


\divider

\cvachievement{\faLaptopCode}{Advanced C\# certificate}{Total Score: \textbf{100/100} (Nov 2015)}

\divider

\cvachievement{\faLaptopCode}{GRE Total Score: 298}{Quant: 159, Verbal:139  }


\iffalse
\cvsection{Referees}

% \cvref{name}{email}{mailing address}
\cvref{Dr. Dara Rahmati}{\href{http://en.sbu.ac.ir/SitePages/Home.aspx}{Faculty of Computer Science and Engineering Shahid Beheshti University}}{dara.rahmati@ipm.ir}


\divider
\cvref{Dr. Saeid Gorgin}{\href{https://irost.org/en/}{Iranian Research Organization for Science and Technology(IROST)}}{gorgin@ipm.ir}
\fi
    
\newpage

\iffalse
\cvsection{References}

% \cvref{name}{email}{mailing address}
\cvref{Prof.\ Alpha Beta}{Institute}{a.beta@university.edu}
{Address Line 1\\Address line 2}

\divider

\cvref{Prof.\ Gamma Delta}{Institute}{g.delta@university.edu}
{Address Line 1\\Address line 2}
\fi
\end{paracol}

\end{document}
